Delayed effects of [responses to?] climate lead to demographic divergence in a fragmented Amazonian landscape

### 2021-05-04 doc/paper.Rmd
change caption objects to unique names

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	fig.path = "figures/",
	message = FALSE,
	warning = FALSE,
	collapse = TRUE,
	comment = "#>",
	dpi = 300
)
library(targets)
library(tidyverse)
library(tsibble)
library(lubridate)
library(knitr)
library(here)
library(patchwork)
```

@@

```{r}
cap <- "Weather normals for Manaus, Brazil (3º6'S, 60º1'W) for 1981–2010. Precipitation (a) shows a marked dry seasons from June through October. Temperature (b) varies less throughout the year. Mean monthly temperature is shown in the solid red line and monthly minimum and maximum temperatures are shown with the lower and upper dashed lines, respectively. Data from Brazilian National Institute of Meterology (INMET)."
```

```{r normals, fig.cap=cap}
normals_plot
```

@@

```{r}
cap <- "Timeseries of demographic parameters and drought ocurrence. Mean plant size ± standard deviation (a) shows that plants were smaller in fragments (red) than continuous forest (blue). (b) shows the survival curve for the 1998 cohort of plants in both fragments and continuous forest. c) shows the proportion of plants with 4 or more shoots flowering each census. In d), monthly 3-month SPEI is plotted. Light grey lines represent values from different grid cells encompassing BDFFP and the dark line is the site mean. Yellow, orange, dark orange, and red stripes show mild, moderate, severe, and extreme drought, respectively."
```

```{r eda, fig.cap=cap, fig.height=7, fig.width=10}
eda_plot
```

@@

```{r}
cap <- "Smooth effect of plant size in the previous census on a) survival, b) log(size), and c) flowering probabiility, modeled by a cubic regression splines. Panel d) shows the smoothed density of different plant sizes in the two habitat types. 95% confidence intervals are shown and include uncertainty in the model intercept and uncertainty due to smoothness selection. The smooths for 1-ha fragments and continuous forest are fit in separate models. The model intercepts were added to the fitted values of the smooth and values are back-transformed to the response scale.  In b), a 1:1 line is shown in dashed red to indicate the line of no growth."
```

```{r size-plot, fig.cap=cap, fig.height=8, fig.width=5}
size_plot
```

```{r}
cap <- "Smooth effect of lagged SPEI on survival in a) continuous forest and b) 1-ha fragments. Surface is modeled as a crossbasis function with cubic regression splines for each marginal basis. Model intercepts were added to fitted values of the crossbasis function and back-transformed to the response scale. Contour lines correspond to a change of 0.002. The bar on the bottom of each panel indicates wet seasons (black, November–May) and dry seasons (white, June–October)."

@@

```{r surv-spei, fig.cap=cap, fig.height=5, fig.width=7}
s_spei_plot
```

@@

```{r}
cap <- "The difference between predicted effects of SPEI history on survival in continuous forest and 1-ha fragments."
```

```{r surv-diff, fig.cap=cap, fig.height=2.5, fig.width=7}
s_spei_diff_plot
```

@@

```{r}
cap <- "Smooth effect of lagged SPEI on plant growth for a) continuous forest and b) 1-ha fragments. Surface is modeled as a crossbasis function with cubic regression splines for each marginal basis. Model intercepts were added to fitted values of the crossbasis function. Contour lines correspond to a change of 0.05. The bar on the bottom of each panel indicates wet seasons (black, November–May) and dry seasons (white, June–October)."
```

```{r growth-spei, fig.cap=cap, fig.height=5, fig.width=7}
g_spei_plot
```

@@

```{r}
cap <- "The difference between predicted effects of SPEI history on plant size in continuous forest and 1-ha fragments."
```

```{r growth-diff, fig.cap=cap, fig.height=2.5, fig.width=7}
g_spei_diff_plot
```

@@

```{r}
cap <- "Smooth effect of lagged SPEI on flowering probability. Surface is modeled as a crossbasis function with cubic regression splines for each marginal basis. Model intercepts were added to fitted values of the crossbasis function and back-transformed to the response scale. Contour lines correspond to a change of 0.001. The bar on the bottom of each panel indicates wet seasons (black, November–May) and dry seasons (white, June–October)."
```

```{r flwr-spei, fig.cap=cap, fig.height=5, fig.width=7}
f_spei_plot
```

@@

```{r}
cap <- "The difference between predicted effects of SPEI history on flowering probability in continuous forest and 1-ha fragments."
```

```{r flwr-diff, fig.cap=cap, fig.height=2.5, fig.width=7}
f_spei_diff_plot
```

@@

# Temporal variation in demographic responses to forest fragmentation

@@

# Delayed effects of climate on demographic vital rates

@@

# Conclusions & Future Directions

@@

@@

### Left-over text

@@

#### Citations / information could allocate to appropriate paragraphs

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	fig.path = "figures/",
	message = FALSE,
	warning = FALSE,
	collapse = TRUE,
	comment = "#>",
	# fig.show = "hide" #hide all figures until the end
	dpi = 300
)
library(targets)
library(tidyverse)
library(tsibble)
library(lubridate)
library(knitr)
library(here)
library(patchwork)
```

@@

```{r}
normals_cap <- "Weather normals for Manaus, Brazil (3º6'S, 60º1'W) for 1981–2010. Precipitation (a) shows a marked dry seasons from June through October. Temperature (b) varies less throughout the year. Mean monthly temperature is shown in the solid red line and monthly minimum and maximum temperatures are shown with the lower and upper dashed lines, respectively. Data from Brazilian National Institute of Meterology (INMET)."
```

```{r normals, fig.cap=normals_cap}
normals_plot
```

@@

```{r}
eda_cap <- "Timeseries of demographic parameters and drought ocurrence. Mean plant size ± standard deviation (a) shows that plants were smaller in fragments (red) than continuous forest (blue). (b) shows the survival curve for the 1998 cohort of plants in both fragments and continuous forest. c) shows the proportion of plants with 4 or more shoots flowering each census. In d), monthly 3-month SPEI is plotted. Light grey lines represent values from different grid cells encompassing BDFFP and the dark line is the site mean. Yellow, orange, dark orange, and red stripes show mild, moderate, severe, and extreme drought, respectively."
```

```{r eda, fig.cap=eda_cap, fig.height=7, fig.width=10}
eda_plot
```

@@

```{r}
size_cap <- "Smooth effect of plant size in the previous census on a) survival, b) log(size), and c) flowering probabiility, modeled by a cubic regression splines. Panel d) shows the smoothed density of different plant sizes in the two habitat types. 95% confidence intervals are shown and include uncertainty in the model intercept and uncertainty due to smoothness selection. The smooths for 1-ha fragments and continuous forest are fit in separate models. The model intercepts were added to the fitted values of the smooth and values are back-transformed to the response scale.  In b), a 1:1 line is shown in dashed red to indicate the line of no growth."
```

```{r size-plot, fig.cap=size_cap, fig.height=8, fig.width=5}
size_plot
```

```{r}
s_spei_cap <- "Smooth effect of lagged SPEI on survival in a) continuous forest and b) 1-ha fragments. Surface is modeled as a crossbasis function with cubic regression splines for each marginal basis. Model intercepts were added to fitted values of the crossbasis function and back-transformed to the response scale. Contour lines correspond to a change of 0.002. The bar on the bottom of each panel indicates wet seasons (black, November–May) and dry seasons (white, June–October)."

@@

```{r surv-spei, fig.cap=s_spei_cap, fig.height=5, fig.width=7}
s_spei_plot
```

@@

```{r}
s_spei_diff_cap <- "The difference between predicted effects of SPEI history on survival in continuous forest and 1-ha fragments."
```

```{r surv-diff, fig.cap=s_spei_diff_cap, fig.height=2.5, fig.width=7}
s_spei_diff_plot
```

@@

```{r}
g_spei_cap <- "Smooth effect of lagged SPEI on plant growth for a) continuous forest and b) 1-ha fragments. Surface is modeled as a crossbasis function with cubic regression splines for each marginal basis. Model intercepts were added to fitted values of the crossbasis function. Contour lines correspond to a change of 0.05. The bar on the bottom of each panel indicates wet seasons (black, November–May) and dry seasons (white, June–October)."
```

```{r growth-spei, fig.cap=g_spei_cap, fig.height=5, fig.width=7}
g_spei_plot
```

@@

```{r}
g_spei_diff_cap <- "The difference between predicted effects of SPEI history on plant size in continuous forest and 1-ha fragments."
```

```{r growth-diff, fig.cap=g_spei_diff_cap, fig.height=2.5, fig.width=7}
g_spei_diff_plot
```

@@

```{r}
f_spei_cap <- "Smooth effect of lagged SPEI on flowering probability. Surface is modeled as a crossbasis function with cubic regression splines for each marginal basis. Model intercepts were added to fitted values of the crossbasis function and back-transformed to the response scale. Contour lines correspond to a change of 0.001. The bar on the bottom of each panel indicates wet seasons (black, November–May) and dry seasons (white, June–October)."
```

```{r flwr-spei, fig.cap=f_spei_cap, fig.height=5, fig.width=7}
f_spei_plot
```

@@

```{r}
f_spei_diff_cap <- "The difference between predicted effects of SPEI history on flowering probability in continuous forest and 1-ha fragments."
```

```{r flwr-diff, fig.cap=f_spei_diff_cap, fig.height=2.5, fig.width=7}
f_spei_diff_plot
```

@@

## Temporal variation in demographic responses to forest fragmentation

@@

## Delayed effects of climate on demographic vital rates

@@

## Conclusions & Future Directions

@@

# Figures

```{r}

@@

# Left-over text

@@

# Citations / information could allocate to appropriate paragraphs
